Exploratory Analysis

### 2025-12-08 Data Cleaning.Rmd

threshold_smallchange <- 0.01

@@

@@

```{r}
write_csv(class_df, "RWAR_dosing_lag_incdec.csv")
```

>>>>

threshold_smallchange <- 0.05

@@

write_csv(rwar_dosing_lag1, )

@@

### Add inc/dec/same for dose

class_df <- lagged_data1

# normal data
class_df$FeCl_change <- ifelse(
    test = abs(class_df$FeCl_change) < 0.01,
    yes = "same",
    no = ifelse(
        test = class_df$FeCl_change < 0,
        yes = "dec",
        no = "inc"
    )
)

# polymer data
class_df$Polymer_change <- ifelse(
    test = abs(class_df$Polymer_change) < 0.01,
    yes = "same",
    no = ifelse(
        test = class_df$Polymer_change < 0,
        yes = "dec",
        no = "inc"
    )
)

class_df
```

### 2025-12-08 Exploratory Analysis Ethan Schilling.Rmd

>>>>

```{r}
library(ggplot2)
library(tidyr)
library(dplyr)

dosing_data <- read_csv("RWAR_dosing_cleaned.csv")

dosing_long <- dosing_data %>%
  pivot_longer(
    cols = starts_with("mean_"),
    names_to = "Characteristics",
    values_to = "Value"
  )

ggplot(dosing_long, aes(x = Timestamp, y = Value, color = Ferric.chloride..mg.L)) +
  geom_point(size = 0.7) +
  facet_wrap(~Characteristics, scales = "free_y") +
  scale_color_viridis_c(option = "plasma") +
  theme_minimal() +
  labs(
    x = "Date",
    y = "Value",
    color = "Ferric Chloride (mg/L)",
    title = "Water Quality Characteristics Over Time by Dosing"
  )
```

### 2025-12-08 Exploratory Analysis.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)

data = read.csv("RWAR_turb_cond_counts_pH_temp.csv")

data$Timestamp = mdy_hm(data$Timestamp)

# Trying to determine what rows have outliers.
# The goal is to go by column, remove outliers & average that day's data, then ultimately combine every column after it's cleaned to create our fully cleaned data frame.
# Then combine with alkalinity and hardness & coagulant doses data??

ggplot(data, aes(x = Timestamp, y = Turbidity..NTU)) +
  geom_point()

data[data$Turbidity..NTU > 10, ] # row 2701 and 5446

ggplot(data, aes(x = Timestamp, y = Conductivity..mS.cm.1)) +
  geom_point()

data[data$Conductivity..mS.cm.1 > 15, ] # row 5270

# Not sure what to do with particle count (PC) data just yet

ggplot(data, aes(x = Timestamp, y = pH..SU)) +
  geom_point()

ggplot(data, aes(x = Timestamp, y = Temperature..deg.C)) +
  geom_point()

>>>>

```{r}
print("GitHub test")
